\papertitle

### 2023-11-14 src/tex/ms.tex
Matching with arXiv

% Import relevant packages
\usepackage{showyourwork}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{multirow}
\usepackage[separate-uncertainty=true]{siunitx}
\usepackage{amsmath}
\usepackage[shortlabels]{enumitem}
\usepackage[page]{appendix}
\usepackage{xfrac}
\usepackage{printlen}
\usepackage[version=4]{mhchem}
\usepackage{blindtext}
\sisetup{
    list-units      = brackets,
    range-units     = brackets,
    range-phrase    = -,
    list-pair-separator= {, },
    list-separator  = {, },
    list-final-separator = {, }
    }
\renewcommand\appendixname{}
\newcommand{\papertitle}{Accurate Estimation of Diffusion Coefficients and their Uncertainties from Computer Simulation}

@@

@@

\let\oldaddcontentsline\addcontentsline
\renewcommand{\addcontentsline}[3]{}

@@

% Author list
\author{Andrew R. McCluskey}
  \email{andrew.mccluskey@ess.eu}
  \affiliation{European Spallation Source ERIC, Ole Maaløes vej 3, 2200 København N, DK}
\author{Samuel W. Coles}
  \affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
  \affiliation{The Faraday Institution, Quad One, Harwell Science and Innovation Campus, Didcot, OX11 0RA, UK}
\author{Benjamin J. Morgan}
  \email{b.j.morgan@bath.ac.uk}
  \affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
  \affiliation{The Faraday Institution, Quad One, Harwell Science and Innovation Campus, Didcot, OX11 0RA, UK}

@@

For data that are both statistically independent and identically normally distributed, ordinary least squares regression (OLS) is unbiased and statistically efficient, and gives accurate estimates of the uncertainties in the resulting regression coefficients.
MSD data obtained from simulation, however, are neither statistically independent nor identically distributed.
The variances, $\var{\oMSDi}$, are correlated, since the displacement of each particle at time $t+\Delta t$ is necessarily similar to its displacement at time $t$, and hence, $\oMSDs{t}$ is similar to $\oMSDs{t+\Delta t}$.
These variances are also typically unequal---the data are heteroscedastic \cite{smith_random_1996,he_statistical_2018}. 
Because the key assumptions of the OLS method are not valid for MSD data, OLS gives statistically inefficient estimates of $\D$, while the estimated regression uncertainties obtained from the standard OLS statistical formulae significantly underestimate the true uncertainty in $\prob{\Dest_\mathrm{OLS}}$ (Fig.~\ref{fig:glswlsols}a).

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/glswlsols.pdf}
    \caption{
        Example distributions of estimated self-diffusion coefficients, $\Dest$, calculated using (a) ordinary least squares (OLS), (b) weighted least squares (WLS), and (c) generalised least squares (GLS),
        from MSD data from \num{4096} individual simulations of \num{128} particles undergoing a \SI{128}{step} 3D lattice random walk, with a step size chosen so that the true diffusion coefficient $\D = 1$.
        In each panel, the grey curve shows the best-fit normal distribution for the simulation data, the upper horizontal bar shows the standard deviation of this distribution, and the lower horizontal bar shows the average estimated standard distribution given by the analytical expression for $\sigma[\prob{\Dest}]$ for each regression method.}
    \label{fig:glswlsols}
    \script{glswlsols.py}
\end{figure}

@@

The estimated variance $\varest{\oMSD}$ can be calculated from a single simulation trajectory, and provides an accurate estimate of the true variance $\var{\oMSD}$.
To demonstrate this, we performed \num{4096} independent simulations of \num{128} particles undergoing a three-dimensional cubic-lattice random walk of \num{128} steps per particle.
Using data from all \num{4096} simulations, we first compute the true simulation MSD and its variance (Fig.~\ref{fig:msd}a).
We also compute the MSD and estimated variance using data from a single simulation trajectory (Fig.~\ref{fig:msd}b), using the scheme described above.
A quantitative comparison between the true MSD variance and the single-trajectory estimated MSD variance is made in Fig.~\ref{fig:msd}c: the close numerical agreement confirms that Eqn~\ref{equ:varestMSD} can be used to estimate $\var{\oMSD}$, which can then be used to parameterise the model covariance matrix $\mathbf{\Sigma^\prime}$ via Eqn.~\ref{equ:cvv}.
%
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/msd.pdf}
    \caption{
        Comparison of the numerical variance in observed MSD from multiple replica simulations and the estimated variance in observed MSD given by rescaling the variance in observed squared displacements (Eqn.~\ref{equ:varestMSD}).
        Panel (a) shows the mean observed MSD from \num{4096} simulations of \num{128} particles undergoing a 3D lattice random walk of \num{128} steps per particle, with error bars of $\pm2\sigma[\oMSDi]$.
        Panel (b) shows the MSD from just one simulation, with error bars of $\pm2\widehat{\sigma}[\oMSDi]$, obtained via Eqn.~\ref{equ:varestMSD}.
        Panel (c) plots the numerical variance against the estimated variance from a single simulation as a function of timestep $i$.
    }
    \label{fig:msd}
    \script{msd.py}
\end{figure}
%

@@

To illustrate the complete numerical procedure for deriving the model covariance matrix, $\bm{\Sigma^\prime}$, we present in Fig.~\ref{fig:covariances} the MSD covariance matrix for \num{4096} random-walk simulations, as described above, at three differing levels of approximation:
the numerically converged covariance matrix, $\bm{\Sigma}$, computed using the data from all \num{4096} simulations (Fig.~\ref{fig:covariances}a);
the corresponding analytical model covariance matrix, $\mathbf{\Sigma^\prime}$, defined by Eqn.~\ref{equ:cvv} and parametrised using analytical variances $\var{\oMSDi}$ (Fig.~\ref{fig:covariances}b); and the average model covariance matrix obtained by parametrising Eqn.~\ref{equ:cvv} using smoothed variances estimated from individual simulation trajectories, and averaging over the resulting set of all \num{4096} matrices (Fig.~\ref{fig:covariances}c).
%
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/covariances.pdf}
    \caption{
        (a) The numerical MSD covariance matrix $\bm{\Sigma}$ calculated using MSD data from \num{4096} simulations of \num{128} particles undergoing a 3D lattice random walk of \num{128} steps per particle.
        (b) The analytical MSD covariance matrix $\bm{\Sigma^\prime}$ (Eqn.~\ref{equ:cvv}), parametrised using analytical random-walk variances $\var{\oMSDi}$.
        (c) The MSD covariance matrix obtained applying the numerical scheme described in the main text to each individual random walk simulation, averaged over all \num{4096} such simulations.
        Colour bars in (a--c) show the covariance, $\Sigma\left[\oMSDi, \oMSDj\right]$.
        The off-diagonal panels show difference plots, computed as per-element ratios between pairs of covariance matrices (a--c).
    }
    \label{fig:covariances}
    \script{covariances.py}
\end{figure}
%

@@

\begin{figure*}[ht!]
    \centering
    \includegraphics[width=\textwidth]{figures/random_walk.pdf}
    \caption{
        (a) Observed MSD from a single simulation of 128 particles undergoing a 3D-lattice random walk of 128 steps per particle (dark line).
        The green shading shows the corresponding posterior distribution $\prob{\model|\oMSD}$ of linear models compatible with the observed MSD data $\oMSD$, calculated using the scheme described in the main text.
        The variegated shading indicates compatibility intervals of \SIlist[list-final-separator = {, and }]{1;2;3}{\sigma}$[\prob{\model|\oMSD}]$.
        (b) The marginal posterior distribution $\prob{\Dest|\oMSD}$ obtained from the posterior distribution of linear models in (a).
        The mean of this distribution gives the point estimate $\Dest$ for this simulation input data.
        The blue horizontal bar shows an interval of one standard deviation in $\prob{\Dest|\oMSD}$.
        (c) Probability distribution of point-estimates $\prob{\Dest}$ obtained from \num{4096} individual random-walk simulations.
        Each simulation has been analysed as in (a) and (b) to yield a single corresponding point estimate $\Dest$.
        The grey line shows the distribution of point estimates, $\prob{\Dest_\mathrm{num}}$, obtained using Bayesian regression with a mean vector and numerical covariance matrix derived from the complete dataset of all \num{4096} simulations.
        The pink horizontal bar shows an interval of one standard deviation in $\prob{\Dest}$.
        (d) Probability distribution of estimated variances, $\varest{\Dest}$, for individual random-walk simulations, compared to the true sample variance (pink vertical line) $\var{\Dest}$.
    } 
    \label{fig:random_walk}
    \script{random_walk.py}
\end{figure*}

@@

We next benchmark our method using data from simulations of the lithium-ion solid electrolyte cubic \ce{Li7La3Zr2O12} (c-LLZO).
We performed a single simulation of \num{1536} atoms (\num{448} Li ions) at \SI{1000}{K} for \SI{1.6}{\nano\second} (full simulation details are provided in the SI).
To generate multiple statistically equivalent trajectories, the resulting simulation data was partitioned into \num{512} effective trajectories, each approximately $\sim\SI{25}{\ps}$ in length, and containing data for \num{56} lithium ions.
We then perform the same approximate Bayesian regression analysis as above on each effective trajectory, excluding the first \SI{10}{ps} of MSD data in each case to remove short-time data corresponding to ballistic and sub-diffusive regimes \cite{he_statistical_2018}.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{figures/diffusion.pdf}
    \caption{
      (a) Probability distribution of point estimates $\prob{\Dest}$ for \num{512} effective simulations of LLZO (orange histogram).
      The grey line shows the distribution $\prob{\Dest_\mathrm{num}}$ obtained using Bayesian regression with the complete LLZO dataset as input.
      The pink bar shows an interval of one standard deviation $\sigma[\prob{\Dest}]$.
      (b) Probability distribution of estimated variances, $\varest{\Dest}$, for individual LLZO effective simulations, compared to the true sample variance (pink vertical line) $\var{\Dest}$.
    }
    \label{fig:diffusion}
    \script{diffusion.py}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{figures/stateff.pdf}
    \caption{
      Scaling of $\var{\Dest}$ with simulation size for OLS (pink), WLS (blue), our approximate Bayesian regression method (green), and GLS (orange).
      (a) Scaling versus number of mobile particles, $N_\mathrm{atoms}$.
      (b) Scaling versus total simulation time, $t_\mathrm{max}$.
      Solid lines show fitted power law relationships for each dataset.
      The WLS and GLS data are obtained using numerically determined variances and covariance, respectively, from a set of \num{512} repeat simulations for each combination of $N_\mathrm{atoms}$ and $t_\mathrm{max}$.
    }
    \label{fig:stat_eff}
    \script{stat_eff.py}
\end{figure}

@@

The approximate Bayesian regression scheme presented here provides a statistically efficient means of estimating the self-diffusion coefficient, $\D$, from molecular dynamics simulation data.
It improves upon textbook approaches by providing accurate point estimates of $\D$ with near-optimal statistical efficiency, while also providing a reasonable description of the uncertainty in these estimates.
The high statistical efficiency of our method allows for the use of smaller simulations, which can significantly reduce computational costs.
Overall, our method offers significant advantages over more conventional methods of estimating self-diffusion coefficients from atomistic simulations.
We have implemented this procedure in the open-source package \textsc{kinisi} \cite{mccluskey_kinisi_2022}, which we hope will support its use within the broader simulation community across a range of materials science contexts.
\section*{Data availability}

Electronic Supplementary Information (ESI) available: A complete set of analysis/plotting scripts allowing for a fully reproducible and automated analysis workflow, using \textsc{showyourwork}~\cite{luger_showyourwork_2021}, for this work is available at Ref.~\cite{mccluskey_github_2022} under an MIT license.
All raw simulation files are available on Zenodo shared under CC BY-SA 4.0 licences, the random walk simulations and other analysis-linked data~\cite{mccluskey_zenodo_2022} and the LLZO raw simulation trajectories~\cite{coles_llzo_zenodo_2022}.
The method outlined in this work is implemented in the open-source Python package \textsc{kinisi}~\cite{mccluskey_kinisi_2022}, which is available under an MIT license.

\section*{CR\lowercase{e}d\lowercase{i}T author statement}

@@

\section{Derivation of the long-time limit covariance matrix for a system of freely diffusing particles.}
\label{sec:ran}
%
In the main manuscript we present the result that the covariance matrix for a system of freely diffusing particles, in the long-time limit, has the form
%
\begin{equation}
  \Sigma^\prime\left[\oMSDi, \oMSDj\right]= \Sigma^\prime\left[\oMSDj, \oMSDi\right] =
  \var{\oMSDi} \frac{\nind{i}}{\nind{j}},\hspace{1em} \forall\,i \leq j,
  \label{equ:cvv_SI}
\end{equation}
%
where $\oMSDi$ is the observed mean-squared displacement (MSD) for time interval $i$ and $\nind{i}$ is the number of statistically independent observed squared displacements averaged over to compute the mean value.

@@

For a single particle undergoing a one-dimensional random walk with step size $\kappa$, each step gives a displacement $h = \pm \kappa$.
After $n$ steps, the MSD, $\oMSDn$, is given by
%
\begin{equation}
  \begin{aligned}
    \oMSDn &= \left[\sum_i^n h_i\right]^2\\
           &= \sum_i^n\sum_j^n h_i h_j \\
           &= \sum_i^n h_i^2 + \sum_i^n\sum_{j\neq i}^n h_ih_j.
  \end{aligned}
\end{equation}
%
The expected MSD in the long-time limit, $\mathbb{E}(\oMSDn) = \moMSDn$, is obtained by averaging over all permutations of $h_i$ and $h_j$:
%
\begin{equation}
  \begin{aligned}
    \moMSDn &= \sum_i^n \left<h_i^2\right> + \sum_i^n\sum_{j\neq i}^n\left<h_i h_j\right>.
  \end{aligned}
\end{equation}
%
For a random walk, the second term averages to zero for all $h_i$ and $h_j$, and
%
\begin{equation}
  \begin{aligned}
    \moMSDn &= \sum_i^n \left<h_i^2\right> \\
            &= n\kappa^2.
  \end{aligned}
  \label{equ:msd_SI}
\end{equation}
%
Hence the expected value for the mean-squared displacement increases linearly with the number of steps taken.

>>>>

% Import relevant packages
\usepackage{showyourwork}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{multirow}
\usepackage[separate-uncertainty=true]{siunitx}
\usepackage{amsmath}
\usepackage[shortlabels]{enumitem}
\usepackage[page]{appendix}
\usepackage{xfrac}
\usepackage{printlen}
\usepackage[version=4]{mhchem}
\usepackage{blindtext}
% \usepackage[hidelinks]{hyperref}
\sisetup{
    list-units      = brackets,
    range-units     = brackets,
    range-phrase    = -,
    list-pair-separator= {, },
    list-separator  = {, },
    list-final-separator = {, }
    }
\renewcommand\appendixname{}
\newcommand{\papertitle}{Accurate Estimation of Diffusion Coefficients and their Uncertainties from Computer Simulation}
% \newcommand{\oMSD}{\ensuremath{\overline{\bm{s}^2}}}
% \newcommand{\oMSDs}[1]{\ensuremath{\overline{s^2}}(#1)}
% \newcommand{\oMSDi}{\ensuremath{\overline{s^2}_i}}
% \newcommand{\oMSDj}{\ensuremath{\overline{s^2}_j}}

@@

\graphicspath{{figures/}}

@@

\let\oldaddcontentsline\addcontentsline% Store \addcontentsline
\renewcommand{\addcontentsline}[3]{}

@@

% Author list
\author{Andrew R. McCluskey}
  \email{andrew.mccluskey@bristol.ac.uk}
  \affiliation{School of Chemistry, University of Bristol, Cantock's Close, Bristol, BS8 1TS, United Kingdom}
  \affiliation{European Spallation Source ERIC, Ole Maaløes vej 3, 2200 København N, DK}
\author{Samuel W. Coles}
  \affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
  \affiliation{The Faraday Institution, Quad One, Harwell Science and Innovation Campus, Didcot, OX11 0RA, UK}
\author{Benjamin J. Morgan}
  \email{b.j.morgan@bath.ac.uk}
  \affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
  \affiliation{The Faraday Institution, Quad One, Harwell Science and Innovation Campus, Didcot, OX11 0RA, UK}

@@

For data that are both statistically independent and identically normally distributed, ordinary least squares regression (OLS) is unbiased and statistically efficient, and gives accurate estimates of the uncertainties in the resulting regression coefficients.
MSD data obtained from simulation, however, are neither statistically independent nor identically distributed.
The variances, $\var{\oMSDi}$, are correlated, since the displacement of each particle at time $t+\Delta t$ is necessarily similar to its displacement at time $t$, and hence, $\oMSDs{t}$ is similar to $\oMSDs{t+\Delta t}$.
These variances are also typically unequal---the data are heteroscedastic \cite{smith_random_1996,he_statistical_2018,UslerEtAl_JComputChem2023}. 
Because the key assumptions of the OLS method are not valid for MSD data, OLS gives statistically inefficient estimates of $\D$, while the estimated regression uncertainties obtained from the standard OLS statistical formulae significantly underestimate the true uncertainty in $\prob{\Dest_\mathrm{OLS}}$ (Fig.~\ref{fig:glswlsols}a).

\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure1.pdf}}
    \includegraphics[width=\columnwidth]{glswlsols.pdf}
    \script{glswlsols.py}
    \caption{
        Example distributions of estimated self-diffusion coefficients, $\Dest$, calculated using (a) ordinary least squares (OLS), (b) weighted least squares (WLS), and (c) generalised least squares (GLS),
        from MSD data from \num{4096} individual simulations of \num{128} particles undergoing a \SI{128}{step} 3D lattice random walk, with a step size chosen so that the true diffusion coefficient $\D = 1$.
        In each panel, the grey curve shows the best-fit normal distribution for the simulation data, the upper horizontal bar shows the standard deviation of this distribution, and the lower horizontal bar shows the average estimated standard distribution given by the analytical expression for $\sigma[\prob{\Dest}]$ for each regression method.}
    \label{fig:glswlsols}
\end{figure}

@@

The estimated variance $\varest{\oMSD}$ can be calculated from a single simulation trajectory, and provides an accurate estimate of the true variance $\var{\oMSD}$.
To demonstrate this, we performed \num{4096} independent simulations of \num{128} particles undergoing a three-dimensional cubic-lattice random walk of \num{128} steps per particle.
Using data from all \num{4096} simulations, we first compute the true simulation MSD and its variance (Fig.~\ref{fig:msd}a).
We also compute the MSD and estimated variance using data from a single simulation trajectory (Fig.~\ref{fig:msd}b), using the scheme described above.
A quantitative comparison between the true MSD variance and the single-trajectory estimated MSD variance is made in Fig.~\ref{fig:msd}c: the close numerical agreement confirms that Eqn~\ref{equ:varestMSD} can be used to estimate $\var{\oMSD}$, which can then be used to parameterise the model covariance matrix $\mathbf{\Sigma^\prime}$ via Eqn.~\ref{equ:cvv}.
%
\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure2.pdf}}
    \includegraphics[width=\columnwidth]{msd.pdf}
    \script{msd.py}
    \caption{
        Comparison of the numerical variance in observed MSD from multiple replica simulations and the estimated variance in observed MSD given by rescaling the variance in observed squared displacements (Eqn.~\ref{equ:varestMSD}).
        Panel (a) shows the mean observed MSD from \num{4096} simulations of \num{128} particles undergoing a 3D lattice random walk of \num{128} steps per particle, with error bars of $\pm2\sigma[\oMSDi]$.
        Panel (b) shows the MSD from just one simulation, with error bars of $\pm2\widehat{\sigma}[\oMSDi]$, obtained via Eqn.~\ref{equ:varestMSD}.
        Panel (c) plots the numerical variance against the estimated variance from a single simulation as a function of timestep $i$.
        %Raw simulation data~\cite{mccluskey_zenodo_2022} and scripts~\cite{mccluskey_github_2022} to generate this figure are available under CC BY 4.0/MIT licences.
    }
    \label{fig:msd}
\end{figure}
%

@@

To illustrate the complete numerical procedure for deriving the model covariance matrix, $\bm{\Sigma^\prime}$, we present in Fig.~\ref{fig:covariances} the MSD covariance matrix for \num{4096} random-walk simulations, as described above, at three differing levels of approximation:
the numerically converged covariance matrix, $\bm{\Sigma}$, computed using the data from all \num{4096} simulations (Fig.~\ref{fig:covariances}a);
the corresponding analytical model covariance matrix, $\mathbf{\Sigma^\prime}$, defined by Eqn.~\ref{equ:cvv} and parametrised using analytical variances $\var{\oMSDi}$ (Fig.~\ref{fig:covariances}b); and the average model covariance matrix obtained by parametrising Eqn.~\ref{equ:cvv} using smoothed variances estimated from individual simulation trajectories, and averaging over the resulting set of all \num{4096} matrices (Fig.~\ref{fig:covariances}c).
%
\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure3.pdf}}
    \includegraphics[width=\columnwidth]{covariances.pdf}
    \script{covariances.py}
    \caption{
        (a) The numerical MSD covariance matrix $\bm{\Sigma}$ calculated using MSD data from \num{4096} simulations of \num{128} particles undergoing a 3D lattice random walk of \num{128} steps per particle.
        (b) The analytical MSD covariance matrix $\bm{\Sigma^\prime}$ (Eqn.~\ref{equ:cvv}), parametrised using analytical random-walk variances $\var{\oMSDi}$.
        (c) The MSD covariance matrix obtained applying the numerical scheme described in the main text to each individual random walk simulation, averaged over all \num{4096} such simulations.
        Colour bars in (a--c) show the covariance, $\Sigma\left[\oMSDi, \oMSDj\right]$.
        The off-diagonal panels show difference plots, computed as per-element ratios between pairs of covariance matrices (a--c).
        %Raw simulation data~\cite{mccluskey_zenodo_2022} and scripts~\cite{mccluskey_github_2022} to generate this figure are available under CC BY 4.0/MIT licences.
    }
    \label{fig:covariances}
\end{figure}
%

@@

\begin{figure*}[ht!]
    \centering
    % \resizebox{\textwidth}{!}{\includegraphics*{figure4.pdf}}
    \includegraphics[width=\textwidth]{random_walk.pdf}
    \script{random_walk.py}
    \caption{
        (a) Observed MSD from a single simulation of 128 particles undergoing a 3D-lattice random walk of 128 steps per particle (dark line).
        The green shading shows the corresponding posterior distribution $\prob{\model|\oMSD}$ of linear models compatible with the observed MSD data $\oMSD$, calculated using the scheme described in the main text.
        The variegated shading indicates compatibility intervals of \SIlist[list-final-separator = {, and }]{1;2;3}{\sigma}$[\prob{\model|\oMSD}]$.
        (b) The marginal posterior distribution $\prob{\Dest|\oMSD}$ obtained from the posterior distribution of linear models in (a).
        The mean of this distribution gives the point estimate $\Dest$ for this simulation input data.
        The blue horizontal bar shows an interval of one standard deviation in $\prob{\Dest|\oMSD}$.
        (c) Probability distribution of point-estimates $\prob{\Dest}$ obtained from \num{4096} individual random-walk simulations.
        Each simulation has been analysed as in (a) and (b) to yield a single corresponding point estimate $\Dest$.
        The grey line shows the distribution of point estimates, $\prob{\Dest_\mathrm{num}}$, obtained using Bayesian regression with a mean vector and numerical covariance matrix derived from the complete dataset of all \num{4096} simulations.
        The pink horizontal bar shows an interval of one standard deviation in $\prob{\Dest}$.
        (d) Probability distribution of estimated variances, $\varest{\Dest}$, for individual random-walk simulations, compared to the true sample variance (pink vertical line) $\var{\Dest}$.
    } 
    \label{fig:random_walk}
\end{figure*}

@@

We next benchmark our method using data from simulations of the lithium-ion solid electrolyte cubic \ce{Li7La3Zr2O12} (c-LLZO).
We performed a single simulation of \num{1536} atoms (\num{448} Li ions) at \SI{1000}{K} for \SI{1.6}{\nano\second} (full simulation details are provided in the Methods section).
To generate multiple statistically equivalent trajectories, the resulting simulation data was partitioned into \num{512} effective trajectories, each approximately $\sim\SI{25}{\ps}$ in length, and containing data for \num{56} lithium ions.
We then perform the same approximate Bayesian regression analysis as above on each effective trajectory, excluding the first \SI{10}{ps} of MSD data in each case to remove short-time data corresponding to ballistic and sub-diffusive regimes \cite{he_statistical_2018}.

@@

\begin{figure}[tb]
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure5.pdf}}
    \includegraphics[width=\columnwidth]{diffusion.pdf}
    \script{diffusion.py}
    \caption{
      (a) Probability distribution of point estimates $\prob{\Dest}$ for \num{512} effective simulations of LLZO (orange histogram).
      The grey line shows the distribution $\prob{\Dest_\mathrm{num}}$ obtained using Bayesian regression with the complete LLZO dataset as input.
      The pink bar shows an interval of one standard deviation $\sigma[\prob{\Dest}]$.
      (b) Probability distribution of estimated variances, $\varest{\Dest}$, for individual LLZO effective simulations, compared to the true sample variance (pink vertical line) $\var{\Dest}$.
      %Raw simulation data~\cite{mccluskey_zenodo_2022} and scripts~\cite{mccluskey_github_2022} to generate this figure are available under CC BY 4.0/MIT licences. 
    }
    \label{fig:diffusion}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure6.pdf}}
    \includegraphics[width=\columnwidth]{stat_eff.pdf}
    \script{stat_eff.py}
    \caption{
      Scaling of $\var{\Dest}$ with simulation size for OLS (pink), WLS (blue), our approximate Bayesian regression method (green), and GLS (orange).
      (a) Scaling versus number of mobile particles, $N_\mathrm{atoms}$.
      (b) Scaling versus total simulation time, $t_\mathrm{max}$.
      Solid lines show fitted power law relationships for each dataset.
      The WLS and GLS data are obtained using numerically determined variances and covariance, respectively, from a set of \num{512} repeat simulations for each combination of $N_\mathrm{atoms}$ and $t_\mathrm{max}$.
    }
    \label{fig:stat_eff}
\end{figure}

@@

The approximate Bayesian regression scheme presented here provides a statistically efficient means of estimating the self-diffusion coefficient, $\D$, from molecular dynamics simulation data.
It improves upon textbook approaches by providing accurate point estimates of $\D$ with near-optimal statistical efficiency, while also providing a reasonable description of the uncertainty in these estimates.
The high statistical efficiency of our method allows for the use of smaller simulations, which can significantly reduce computational costs.
Overall, our method offers significant advantages over more conventional methods of estimating self-diffusion coefficients from atomistic simulations.
We have implemented this procedure in the open-source package \textsc{kinisi} \cite{mccluskey_kinisi_2022}, which we hope will support its use within the broader simulation community across a range of materials science contexts.

\section{Methods}

\subsection{Numerical implementation in KINISI}
\label{sec:implementation}
We have implemented the approximate Bayesian estimation method described in the main text in the open-source Python package \textsc{kinisi}~\cite{mccluskey_kinisi_2022}. 
This section provides numerical details regarding the implementation of this method.

\subsection{LLZO simulations}
Classical molecular dynamics were run using the \textsc{metalwalls} code~\cite{marin_metalwalls_2020}. 
We used the DIPPIM polarisable ion force field, as parameterised by Burbano \emph{et al.}~\cite{burbano_sparse_2016}, due to its proven accuracy in accounting for the effect of ion polarisability on diffusion~\cite{wilson_polarization_1993,burbano_sparse_2016}. 
We simulated the cubic phase of LLZO in NVT ensemble at a temperature of \SI{1000}{\kelvin}.
Simulations were run for \SI{2}{\nano\second} with a \SI{2}{\femto\second} timestep. 
To control temperature, we used a Nos\'{e}-Hoover thermostat, with a relaxation time of \SI{121}{\femto\second} (5000 $\hbar / E_{h}$)~\cite{nose_unified_1984,hoover_canonical_1985,martyna_nose_1992}. 
Simulations were performed using $2 \times 2 \times 2$ supercells with \SI{1536}{atoms} following the same protocol as in Ref.~\citenum{burbano_sparse_2016}.

\section*{Data \& Code Availability}

Electronic Supplementary Information (ESI) available: A complete set of analysis/plotting scripts allowing for a fully reproducible and automated analysis workflow, using \textsc{showyourwork}~\cite{luger_showyourwork_2021}, for this work is available at Ref.~\cite{mccluskey_github_2022} under an MIT license.
All raw simulation files are available on Zenodo shared under CC BY-SA 4.0 licences, the random walk simulations and other analysis-linked data~\cite{mccluskey_zenodo_2022} and the LLZO raw simulation trajectories~\cite{coles_llzo_zenodo_2022}.
The method outlined in this work is implemented in the open-source Python package \textsc{kinisi}~\cite{mccluskey_kinisi_2022}, which is available under an MIT license, and can be accessed via \url{https://github.com/bjmorgan/kinisi}.

\section*{CR\lowercase{e}d\lowercase{i}T Author Statement}

@@

\section{Derivation of the long-time limit covariance matrix for a system of freely diffusing particles.}
\label{sec:ran}
In the main manuscript we present the result that the covariance matrix for a system of freely diffusing particles, in the long-time limit, has the form
\begin{equation}
  \Sigma^\prime\left[\oMSDi, \oMSDj\right]= \Sigma^\prime\left[\oMSDj, \oMSDi\right] =
  \var{\oMSDi} \frac{\nind{i}}{\nind{j}},\hspace{1em} \forall\,i \leq j,
  \label{equ:cvv_SI}
\end{equation}
where $\oMSDi$ is the observed mean-squared displacement (MSD) for time interval $i$ and $\nind{i}$ is the number of statistically independent observed squared displacements averaged over to compute the mean value.

@@

For a single particle undergoing a one-dimensional random walk with step size $\kappa$, each step gives a displacement $h = \pm \kappa$.
After $n$ steps, the MSD, $\oMSDn$, is given by
\begin{equation}
  \begin{aligned}
    \oMSDn &= \left[\sum_i^n h_i\right]^2\\
           &= \sum_i^n\sum_j^n h_i h_j \\
           &= \sum_i^n h_i^2 + \sum_i^n\sum_{j\neq i}^n h_ih_j.
  \end{aligned}
\end{equation}
The expected MSD in the long-time limit, $\mathbb{E}(\oMSDn) = \moMSDn$, is obtained by averaging over all permutations of $h_i$ and $h_j$:
\begin{equation}
  \begin{aligned}
    \moMSDn &= \sum_i^n \left<h_i^2\right> + \sum_i^n\sum_{j\neq i}^n\left<h_i h_j\right>.
  \end{aligned}
\end{equation}
For a random walk, the second term averages to zero for all $h_i$ and $h_j$, and
\begin{equation}
  \begin{aligned}
    \moMSDn &= \sum_i^n \left<h_i^2\right> \\
            &= n\kappa^2.
  \end{aligned}
  \label{equ:msd_SI}
\end{equation}
Hence the expected value for the mean-squared displacement increases linearly with the number of steps taken.

The variance in the observed MSD, $\var{\oMSDn}$, is given by the standard statistical formula
\begin{equation}
    \var{\oMSDn} = \left<{\left[\oMSDn - \moMSDn\right]}^2\right>,
\end{equation}
which can be expanded as
\begin{equation}
    \begin{aligned}
        \var{\oMSDn} &= \left<\oMSDn^2\right> - 2\moMSDn\left<\oMSDn\right> + \moMSDn^2,\\
                     &= \left<\oMSDn^2\right> - \moMSDn^{\,2}.
    \end{aligned}
\end{equation}
The first term can be expanded in terms of displacements $h$ as
\begin{equation}
  \left<\oMSDn^2\right> = \left<\sum_i^n\sum_j^n\sum_k^n\sum_l^n h_i h_j h_k h_l\right>,
  \label{equ:big_av}
\end{equation}
which can be simplified by noting that $h_i$, $h_j$, $h_k$, and $h_l$ are uncorrelated when $i \neq j \neq k \neq l$, and the only terms that contribute to the average are those where $h_ih_jh_kh_l$ is guaranteed to be non-zero:
\begin{itemize}
    \item[(a)] $i = j = k = l$;
    \item[(b)] $(i = j) \neq (k = l)$;
    \item[(c)] $(i = k) \neq (j = l)$;
    \item[(d)] $(i = l) \neq (j = k)$. 
\end{itemize}
From (a) we obtain
\begin{equation}
    \left<\sum_i^nh_i^4\right> = n\kappa^4,
\end{equation}
and from (b), (c), and (d), which are equivalent, we obtain
\begin{equation}
    \left<\sum_i^n\sum_j^nh_i^2h_j^2\right> = (n\kappa^2)^2 = n^2\kappa^4.
\end{equation}
This gives
\begin{equation}
    \left<\oMSDn^2\right> = (3n^2 + n)\kappa^4,
\end{equation}
which, in the limit $n \to \infty$, approaches
\begin{equation}
    \left<\oMSDn^2\right> = 3n^2\kappa^4.
    \label{equ:infty}
\end{equation}
Combining this result with Eqn.~\ref{equ:msd_SI}, we can express the variance in the mean-squared displacement as
\begin{equation}
    \var{\oMSDn} = 3n^2\kappa^4 - n^2\kappa^4 = 2n^2\kappa^4,
    \label{equ:varmsd}
\end{equation}
i.e., $\var{\oMSDn}$ increases quadratically with the number of steps taken, or, equivalently, with time.

Eqn.~\ref{equ:varmsd} gives the variance of the mean squared displacement for a single particle considering a single time-origin.
We can obtain improved statistics by averaging over statistically equivalent observed squared displacements (see Eqn.~2 in the main text), which can be achieved by averaging over mobile particles or by averaging over time origins.
This averaging over equivalent observations reduces the variance in the observed MSD to
\begin{equation}
    \var{\oMSDn} = \frac{2n^2\kappa^4}{\nind{n}},
\label{equ:der_var}
\end{equation}
where $\nind{n}$ is the total number of statistically independent squared displacements that contribute to $\oMSDi$.
In the long-time limit, $\nind{n}$ is given by the product of the number of mobile particles and the number of non-overlapping time-windows of length $i$ in our simulation trajectory.
Note that $\nind{n}$ considers non-overlapping time windows, since mutually overlapping time-windows give correlated squared displacements.

The results for a one-dimensional lattice above (Eqns.~\ref{equ:msd_SI} \&~\ref{equ:der_var}) can be extended to a $d$-dimensional lattice, to give
\begin{equation}
    \moMSDn_{d} = \sum^d{\frac{n\kappa^2}{d}} = n\kappa^2,
\end{equation}
with variance
\begin{equation}
    \var{\oMSDn}_d = \sum^d{\frac{2n^2\kappa^4}{d^2\nind{n}}} = \frac{2n^2\kappa^4}{d\nind{n}},
\end{equation}
Because each step is equally likely to move a particle along each of the $d$ dimensions, the term $n$ in Eqns.~\ref{equ:msd_SI} \&~\ref{equ:der_var} is replaced here with $n/d$.
